### 2021-11-05 plos_latex_template.tex
Laura Ación on hybrid conferences

% Rocío: Idea of this paragraph: tips to make a diverse and inclusive team work + paying them
When working with people from marginalized groups do not assume that self-nomination and voting will work as mechanisms to choose leadership positions. Instead, nominate directly and offer leading positions that would normally be occupied by people from privileged groups.
Build an environment in which every person can express their position and give priority to people from systematically excluded groups.
Many people lack the institutional support to put time and effort into the organization tasks and do not have the luxury to commit to the organization for free; consider paying them as an item in your budget.  
In addition, tasks such as receiving and responding to Code of Conduct reports can be emotionally intense work and should be additionally rewarded.

@@

@@

%an online component is not inclusive \textit{per se} without taking many other precautions

>>>>

% Rocío: Idea of this paragraph: tips to make a diverse and inclusive team work + paying them
When working with people from marginalized groups do not assume that self-nomination and voting will work as mechanisms to choose leadership positions. Instead, nominate directly and offer leading positions that would normally be occupied by people from privileged groups.
Build an environment in which every person can express their position and give priority to people from systematically excluded groups.
Many people lack the institutional support to put time and effort into the organization tasks and do not have the luxury to commit to the organization for free; consider paying them as an item in your budget.

% Saranjeet: At times regional institutes and universities do not support nor recognize the time put in organization tasks. As such one needs to carry out their day work for the institute while working extra hours for organizing. It might be challenging to find a way to recognize organizers that works internationally. However, there should certainly be some mechanism put into place which recognizes the time of the organizers.
In addition, tasks such as receiving and responding to Code of Conduct reports can be emotionally intense work and should be additionally rewarded.

@@

%Saranjeet: About time zones, although we can rotate and have different days dedicated to different time zones, we could also try spreading the conference time to be longer. So that each day the conference runs live for a couple of hours or so and the recorded material is made available/uploaded on YouTube (say) soon (every day). This might help because, not everyone might have the luxury of attending 4-6 hours of the conference on a weekday, even though it is running in their local timezone. However, people might be able to attend a couple of hours even on weekdays and will not get the feeling that they have missed a huge chunk of the conference.

% Saranjeet: Not to include in this paper, but a general suggestion. Why not select a platform which helps in live broadcasting of the conference on LinkedIn as well? For example, Streamyard (https://streamyard.com/) is one such multistreaming platform, that can simultaneously stream to YouTube, LinkedIn, Twitter, and other platforms

@@

In fact, experts in theorizing about and building communities of practice [Wenger, 1999] who have been holding hybrid events since 2011 [Wenger-Tayner, 2021] consider that inclusive hybrid events are the future. These authors emphasize the need that all participants of hybrid events must go through the same event quality to the point that in-person and online participants pay the same registration amount to participate in high-quality hybrid conferences. These authors recommend having a buddy system, where every person attending online has an in-person attendant that makes sure the online person can follow the event and participate in the event as if they were in the room [Wenger-Trayner, 2020]. Wenger-Trayner (2020, 2021) also recommends having a chat function for back-channel conversations between all attendants, a virtual space for all online attendants to talk to each other, and allocating time to small group conversations, often mixing in-person and online groups. The physical venue will have to include multiple ways to connect with online folks such as tablets on the meeting venue tables and cameras that allow online attendants to follow who is speaking in the in-person space. 
%an online component is not inclusive \textit{per se} without taking many other precautions
